\documentclass[a4paper, 12pt]{article}
\title{True Computer Vision}
\author{Supratik Chatterjee}
\begin{document}
\chapter{Research Statement}
Computational Creativity and it's applications in Computer Vision.

The majority bulk of algorithms that are there on Computer Vision focus primarily on object recognition, which is enabled through pre-existent data.

The questions that I wish to ask and answer are the following ; 

\begin{enumerate}
    \item Can computers be taught to differentiate objects, by themselves?
    \item Can the accuracy of a camera be leveraged to perform a human-like scan?
    \item What are the processing constraints required for human like vision?
    \item What are the easiest ways of identifying the distance between the vision system and the target?
    \item Is a single system capable of making annotation areas possible?
\end{enumerate}

For the first question, the way humans do it is that we understand what an 'object' is, 
since we can feel it to understand it better. But how does a computer, limited only to the camera itself,
be capable of recognizing objects as a whole?

We can be shown a part of an object, and understand that it is a part of a recognizable image.
Computers can be trained to look for the same. But for impactful requirements, we cannot train it for every new thing as well.

You have a commercial car security wishes to track, they would have to feed the data for the exact make and model to track.

You want a system that analyzes aberations, what about large outlier aberations?
Will it be able to recognize and handle accordingly?

Most systems are incapable of identifying an object by itself, which essentially stems from the lack of creativity, or 
evolutionary design in the sensor system.

How do we change that to make a system capable of actually seeing?

\chapter{Facts}

\chapter{Distance estimation}

Ideas : 
\begin{enumerate}
    \item Pythagorean method, using altimeter and angle from a accelerometer, to target in the middle.
    \item Focal length based estimation
    \item Stereographic depth estimation
\end{enumerate}

\chapter{Human Like Vision}

Vision in humans work in 2 ways.

\begin{enumerate}
    \item Either focus on some particular segments of the image rather than everything the eyes see
    \item Focus on full input, or what can be termed as focusing on peripheral vision
\end{enumerate}


I

\end{document}